Increasing Productivity Amid Stable Nutrient Regimes in Rhode Island Lakes and Reservoirs

### 2019-05-21 manuscript/manuscript.Rmd
bit more on discussion

In addition to the annualized trends we address with this study, there are other trends that may be of interest.  First, what are the trends for water quality at finer temporal scales such as monthly or seasonal trends?  Anecdotal evidence in Rhode Island [SHOULD REFERENCE THIS SOMEHOW] points to greater increases in temperature earlier and later in the growing season and suggests a lengthening of the growing season.  Second, are trends influenced by the current state of a given waterbody?  For instance, are oligotrophic lakes showing stronger trends than eutorphic lakes or are all lakes showing similar trends regardless of current trohpic status?  These questions all warrant further investigation.

@@

- Provides feedback on long term changes for managers and stakeholders
- Season Length Changes
- How to stabilize trends?  
    - More reductions in nutrients?  
    - Engineered solutions to slow warming? 
    - Look to individual lakes that buck the trend for suggestions (e.g. local landcover may provide a buffer)
    - stable nutrients doesn't mean they are low, just not getting worse
    - interventions to reduce nutrients could offset the suggested increase caused by temperature
        - e.g. freshwater mussels restoration

>>>>

In addition to the annualized trends we address with this study, there are other trends that may be of interest.  First, what are the trends for water quality at finer temporal scales such as monthly or seasonal trends?  Anecdotal evidence in Rhode Island [SHOULD REFERENCE THIS SOMEHOW] points to greater increases in temperature earlier and later in the growing season and suggests a lengthening of the growing season. Furthermore, preliminary analysis of the URIWW data back this up with mean temperature for May 1993 to May 1995 cooler by nearly a degree than mean temperature for May 2014 through May 2016.  Second, are trends influenced by the current state of a given waterbody?  For instance, are oligotrophic lakes showing stronger trends than eutorphic lakes or are all lakes showing similar trends regardless of current trohpic status?  These questions all warrant further, careful investigation.

@@

- Provides feedback on long term changes for managers and stakeholders
- Season Length Changes
- How to stabilize trends?  
    - More reductions in nutrients?  
    - Engineered solutions to slow warming? 
    - Look to individual lakes that buck the trend for suggestions (e.g. local land cover may provide a buffer)
    - stable nutrients doesn't mean they are low, just not getting worse
    - interventions to reduce nutrients could offset the suggested increase caused by temperature
        - e.g. freshwater mussels restoration
